Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-09 doc/main_jfm.tex
adding movie captions
update table 1
working on revision

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}
%
\usepackage[justification=justified]{caption}

@@

\begin{table}
\caption{Friction Coefficients}
\centering
\begin{tabular}{c c c c c c c c }
 $\dot\gamma$  (ns$^{-1}$) & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
\hline                    
%$\dot\gamma$ (ns$^{-1}$)        & 0.0033 & 0.0041 & 0.0049 & 0.0057 & 0.0066 & 0.0074 & 0.0082\\
%$F_{f}$ (pN nm$^{-1}$)           & 1.84 & 4.90 & 11.36 & 8.16 & 6.14 &  17.69 &  24.33 \\[1ex]
%$\dot\theta$ (nm ns$^{-1}$)           & $6.84\times10^{-5}$ & $1.31\times10^{-4}$ & $3.46\times10^{-4}$ & $2.32\times10^{-4}$ & $1.81\times10^{-4}$ & $4.91\times10^{-4}$ & $5.83\times10^{-4}$\\ [1ex]
%$b$ (pN$\cdot$ns nm$^{-3}$)    & 0.22 & 0.87*  & 0.22 &0.21 & 1.29* & 0.31 & 0.30\\ 
$b$ (pN ns nm$^{-3}$)    & 0.43 & 1.19 &   0.42  & 0.69 &   0.97  &   0.80  &  1.07 \\ 
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
over a range of shear rates
which is in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d).

@@

@@

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\usepackage{todonotes}

%
\usepackage[justification=justified]{caption}

@@

%original table
%\begin{table}
%\caption{Friction Coefficients}
%\centering
%\begin{tabular}{c c c c c c c c }
% $\dot\gamma$  (ns$^{-1}$) & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  \\
%\hline                    
%$b$ (pN ns nm$^{-3}$)    & 0.43 & 1.19 &   0.42  & 0.69 &   0.97  &   0.80  &  1.07 \\ 
%\hline    
%\end{tabular} 
%\label{table1}
%\end{table}

%updated table
\begin{table}
\caption{Friction Coefficients $b$ (pN ns nm$^{-3}$) \\
}
\centering
\begin{tabular}{c c c c c c c c c }
& & & & $\dot\gamma$  (ns$^{-1}$) & & & &\\
\cline{2-8}\\
 & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
\cline{1-8}\\
$N_b=53$  & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  \\ 
$N_b=56$ & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
$N_b=58$   & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
$N_b=61$  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\ 
\end{tabular} 
\label{table1}
\end{table}

@@

%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the default number of particles is $N_b = 58$. With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
With $\{-10\%,-5\%, 5\%\}$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{53,56,58\}$, respectively. }
%
Over a range of shear rates
which is in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d).

@@

% table 2

\begin{table}
\caption{Stretching Moduli and Permeabilities}
\centering
\begin{tabular}{ c c c c c c c }
 radius ($l_0$) &  $\rho$ ($l_0$)  &  $\rho_0$ ($l_0$) &  $M (k_BT)$ & $\gamma$ (pN nm$^{-1})$ & $K_A$ (pN nm$^{-1}$) & $P$ (nm$^3$ ns$^{-1}$pN$^{-1}$) \\
\hline      \hline 
 0.5 & 2.0  &   0.5  & 4.0 &  4.1  & 170$\pm9$   &  0.0296\\ 
%
 0.475 & 1.9  &   0.475  & 4.0 &  4.1   & 184$\pm5$  &  0.0283 \\ 
%
 0.45 & 1.8  &   0.45  & 4.0   &  4.1   & 189$\pm6$  &  0.0252  \\ 
%
 0.5 & 2.0  &   0.5  & 4.2   &  4.31  & 185$\pm5$  &  0.0292  \\ 
%
 0.5 & 2.0  &   0.5  & 4.4   &  4.51  & 195$\pm5$  &  0.0294 \\ 
\end{tabular} 
\label{table2}
\end{table}

@@

% Supplementary Materials
\input{Supplementary}
